Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-05-21 content.tex
Add note for Rampal

From the twin tree, we simulate an alignment following the same
history as the twin tree, with the addition that 
the same total number of mutations have
taken place from root sequence to the sequences in the present.
This addition assures there is the same amount of historical information
stored in the alignments of both the true and twin alignment.
We achieve this by simply simulating twin alignments up until we
obtain one that has the desired number of mutations.

>>>>

\richel{New section about equal number of mutations}
From the twin tree, we simulate an alignment following the same
history as the twin tree, with the addition that 
the same total number of mutations have
taken place from root sequence to the sequences in the present.
This addition assures there is the same amount of historical information
stored in the alignments of both the true and twin alignment.
We achieve this by simply simulating twin alignments up until we
obtain one that has the desired number of mutations.
